\section{Related Works}

The two papers which we have chosen are different methodologies to implement cloud authentication using NFC tags and the devices scanning them. The first paper focuses on authenticating transactions using NFC payment terminals to initiate the authentication. A hash value is created from a timestamp and a random value from the terminal. The second paper uses an NFC tag instead of a terminal. In this paper, a hash is created from the tag ID and a random number which is stored on the tag itself and updated through the algorithm. We will be focusing on implementing our version of the second paper.\\

Our first paper is \emph{A Cloud-Based Secure Authentication Protocol for Contactless-NFC Payment}, this paper proposes an authentication protocol for payment systems~\cite{7335332}. This paper proposes an alternative to the standard Europay Mastercard Visa (EMV) protocol currently used around the world to authenticate credit cards using NFC. The second papers we are examining are \emph{Secure and Lightweight Authentication Protocol for NFC Tag-Based Services} which proposes an authentication tool that is lightweight and able to authenticate both tags and devices using a server~\cite{7153937}. The main goal of this protocol is to authenticate a device is at an NFC tag to do something such as open a door or confirm a device’s location. Using this paper, we will attempt to duplicate their authentication process using our own NFC Tags and readers.\\

The two papers mentioned are using the same technology to authenticate the information transferred between NFC Tags and NFC Readers/Payment systems. Both protocols proposed are trying to be secure to protect people’s data while also being efficient. This is an important security topic as many Asian, European countries, as well as Canada, have been using NFC payment protocols to authenticate credit and debit cards. As this becomes more commonplace, more effort will need to be put in place to secure these systems and make sure.
